MLISA: Machine Learning-based \\ Intelligent Service Agents (to change)

### 2014-07-13 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{MLISA: Machine Learning-based \\ Intelligent Service Agents}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

@@

The goal of all parties involved in the community is to maximize their long-term outcome of their collaboration. Web services need to be utilized with a selection strategy to choose from all the different possible collaboration groups they can form and also an estimation method for evaluating the long-term gain of joining different possible communities. Web services need to experiment different possible collaborative groups with other web services in order to be able to estimate their gain over time. However with high number of possible communities and many other business restrictions its not possible to test run collaboration with random web services. Even if a linear approximate function for estimating utility base on community web services' parameters is adopted, the exponential \footnote{Bell number: $http://en.wikipedia.org/wiki/Bell_number$} growth rate of possible number of partition of web services into communities, would make any brute-force type algorithm for best community selection strategy non-practical in practice.

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{MLISA: Machine Learning-based \\ Intelligent Service Agents (to change)}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

@@

The goal of all parties involved in the community is to maximize their long-term outcome of their collaboration. Web services need to be utilized with a selection strategy to choose from all the different possible collaboration groups they can form and also an estimation method for evaluating the long-term gain of joining different possible communities. Web services need to experiment different possible collaborative groups with other web services in order to be able to estimate their gain over time. However with high number of possible communities and many other business restrictions its not possible to test run collaboration with random web services. Even if a linear approximate function for estimating utility base on community web services' parameters is adopted, the exponential \footnote{Bell number: $http://en.wikipedia.org/wiki/Bell_number$} growth rate of possible number of partition of web services into communities, would make any brute-force type algorithm for best community selection strategy intractable and non-practical in applications.
